One Model May Not Fit All: Subgroup Detection Using Model-Based Recursive Partitioning

### 2023-10-26 Raschtree_MH.Rnw
Final Changes Raschtree Part

<<echo = FALSE>>=
load("SPISA_example/dat_SPISA.rda")
covar_data$Student <- NULL
covar_data$Occupation <- NULL
covar_data$Area <- sub("\n", "", covar_data$Area)
dat_SPISA <- covar_data
dat_SPISA$culture <- culture_scale
save(dat_SPISA, file = "dat_SPISA.Rda")
@

We will illustrate the usage of Rasch trees and the Mantel-Haenszel effect size measure by means of a dataset from \citet{SPISA:book}. An online general knowledge quiz was conducted by the German
weekly news magazine SPIEGEL. Below we will use the abbreviation \texttt{SPISA} for the name of the data set, because the quiz was termed ``students' PISA'' by the magazine, but it is not related to the ``real'' PISA study by the OECD. The data set contains the quiz results as well as
sociodemographic data. In the following we will use only the responses to the nine items of the \textit{culture} scale (i.e., items 28 through 36) from test booklet 20 and only the $\Sexpr{nrow(covar_data)}$ complete cases of university students for illustration. The wording of the items is provided in Appendix~\ref{sec:AppendixB}.

@@

\todo[inline]{I suggest that we publish the data set Mirka created with the paper, but don't show her data preprocessing steps (which are in the echo = FALSE chunk above); I usually use load for Rda files, Marjolein uses readRDS, is there an advantage? use the same in both examples.
Mirka: from what I understand, readRDS is for loading .rds/.rda files with only one r object in it, while load is for .rda files with one or more r object in it. I would opt for .rda, because I think it is more general? }

@@

<<echo = FALSE>>=
if(!file.exists("SPISA_example/Raschtree.rda")){
  library("psychotree")
  Raschtree_culture <- raschtree(culture ~  Gender + Age + Area,
                                 data = dat_SPISA)
  save(Raschtree_culture, file = "SPISA_example/Raschtree.rda")
}
load("SPISA_example/Raschtree.rda")
@

@@

<<echo = FALSE>>=
if(!file.exists("SPISA_example/Raschtree.rda")){
  pdf("raschtree_culture.pdf", width = 36, height = 15)
  plot(Raschtree_culture)
  dev.off()
}
@

<<fig = TRUE, width = 15, height = 8, eval = FALSE>>=
plot(Raschtree_culture)
@

% \begin{figure}[!h]
% \centering
% \includegraphics[width = \textwidth]{raschtree_culture.pdf}
% \end{figure}

>>>>

<<echo = FALSE>>=
load("dat_SPISA.Rda")
@

We will illustrate the usage of Rasch trees and the Mantel-Haenszel effect size measure by means of a dataset from \citet{SPISA:book}. An online general knowledge quiz was conducted by the German
weekly news magazine SPIEGEL. Below we will use the abbreviation \texttt{SPISA} for the name of the data set, because the quiz was termed ``students' PISA'' by the magazine, but it is not related to the ``real'' PISA study by the OECD. The data set contains the quiz results as well as
sociodemographic data. In the following we will use only the responses to the nine items of the \textit{culture} scale (i.e., items 28 through 36) from test booklet 20 and only the $\Sexpr{nrow(dat_SPISA)}$ complete cases of university students for illustration. The wording of the items is provided in Appendix~\ref{sec:AppendixB}.

@@

\todo{I usually use load for Rda files, Marjolein uses readRDS, is there an advantage? use the same in both examples.
Mirka: from what I understand, readRDS is for loading .rds/.rda files with only one r object in it, while load is for .rda files with one or more r object in it. I would opt for .rda, because I think it is more general? }

@@

<<echo = FALSE>>=
library("psychotree")
if(!file.exists("SPISA_example/Raschtree.rda")){
  # relabel factors of the area covariate so that the Raschtree is not too big: 
  levels(dat_SPISA$Area) <- c("Lang & Cult", "\nLaw and Econ",
                              "\nMed & Health", "\nEngin",
                              "\nSci, Phar, Geo",
                              "\nAgri & Nutri",
                              "\nSports", "Arts",
                              "\nno Info")
  Raschtree_culture <- raschtree(culture ~  Gender + Age + Area,
                                 data = dat_SPISA)
  save(Raschtree_culture, file = "SPISA_example/Raschtree.rda")
}
load("SPISA_example/Raschtree.rda")
@

@@

<<fig = TRUE, width = 22, height = 10>>=
plot(Raschtree_culture)
@
